### 2021-07-17 chapters/10_related_work.tex
minor changes

\subsection{Clustering overlapped mutants}
\label{ch:overlapping_mutants}
Ma et al., clustered mutants by overlap\cite{Ma2016}.
They defined the term overlap as as mutants that are functionally equivalent.
This is close to an equivalent mutant but not the same.
They explain that an equivalent mutants is functionally identical to the original source code while an overlapped mutant is functionally identical to at least one other mutant.
If a mutant does not have an overlapped mutant that mutant would be a cluster on its own.
The achieved a reduction, in mutants executed, of 10\%.
They write in their research that it is limited to the mutator operators on expression level. 
If a mutator did not generate two or more mutants they could not detect overlapping mutants.
Their future work includes adding more mutators and widening the scope level to statements or blocks.
\newline
The research does not include efficiency.
While they show that they can cluster mutants based on overlap they do not show how efficient the mutation testing process is compared to executing a full set of mutants.
A threat to their validity, which is not addressed, is the fact that two overlapping mutants may not be challenged by the same tests and thus can result in different results.
Our research solves this problem by taking into account the location of the mutants.
Chapter \ref{ch:characteristics_location} describes what characteristics we use.

\subsection{Clustering by scope}
Yu et al., extended the research about overlapping mutants(See chapter \ref{ch:overlapping_mutants})\cite{Yu2019PossibilityScope}.
They extended the scope by adding more mutators.
The also extended the research to include statements and blocks.
Their results shows an increase in clustered mutants.
The research of Yu et al., suffers from the same limitations and threats  mentioned in Chapter \ref{ch:overlapping_mutants}.

\subsection{Clustering Hamming distance}
Ji et al., did a qualitative domain analysis on mutants\cite{Ji2009}.
As a result they identified the Hamming distance to cluster with. 
The Hamming distance is, like the Levenshtein distance, a similarity measure.
They use the k-means algorithm to cluster mutants represented by Hamming distance.
They write that the reduced test set in their experiment is still as strong as the original test set\cite{Ji2009}.
\newline
Ji et al., were successful in clustering mutants with Hamming distance and the k-means algorithm.
They do acknowledge that their research still has problems with rationally determining the domains of their clusters.
Our research does not have this problem, as the centre of the domains are decided by the characteristics of the mutants.

\subsection{Spectral clustering}
Wei et al., makes use of an intelligent technique, namely spectral clustering, to improve the efficacy of mutant reduction\cite{Wei2021SpectralTesting}.
They defined multiple definitions for the mutants; similarity distance, distance between the mutants and a killing matrix of the mutants.
With these definitions they reduced the mutants based on their proposed reduction method.
This method is based on spectral clustering (SCMT), the determination method of the number of clusters, spectral clustering of mutants, and selection of representative mutants.
The reduced mutants were then clustered with a classical clustering algorithm.
Their results are promising and show high cluster accuracy.
They write that there is still work left to do in optimizing the matrices and clustering algorithms.
Our goal overlaps with that of Wei, the difference is that we used a different methodology to achieve that goal.
Another difference is that our research does not require to know the result of a mutant(killed or survived).

\subsection{Clustering similarity}
Hussain et al., used the k-means and agglomerative clustering algorithm to cluster the mutants according to a similarity measure. 
They used the Hamming distance as similarity measure.
They calculated the distance and used this as data to feed into the clustering algorithms.
The number of clusters and the initial position of the cluster center in the k-means algorithm are difficult to determine, and the process of the agglomerative clustering algorithm makes it difficult to correct the existing cluster formation\cite{Hussain2008}.
They did take into account efficiency.
Hussain et al, had the same goals as our research. 
The difference is that our research used different and more elaborated methods to cluster the mutants.
Hussain et al., calculated the mutation score by counting one cluster as one mutant.
Our research calculated a weighted mutation score to reflect the clusters more accurately.

\subsection{Generalizing mutants}
Wilinski et al., tried to generalize the mutants by defining metrics.
Each metric is calculated for a specific mutator.
The three metrics are usefulness, frequency and dependency.
Combining the results of usefulness and frequency metrics, they observed that reducing the number of generated mutants gives noticeable cost reduction without a loss of the mutation score accuracy.
Wilinski et al., their research is narrowly scoped to the specific mutators they decided to do research on.
Our research does not contain this limitation.
The mutator is used as a characteristic in our research instead of limiting our research it helps define a mutant.

>>>>

\section{Clustering overlapped mutants}
\label{ch:overlapping_mutants}
Ma et al., clustered mutants by overlap\cite{Ma2016}.
They defined the term overlap as as mutants that are functionally equivalent.
This is close to an equivalent mutant but not the same.
They explain that an equivalent mutants is functionally identical to the original source code while an overlapped mutant is functionally identical to at least one other mutant.
If a mutant does not have an overlapped mutant that mutant would be a cluster on its own.
The achieved a reduction, in mutants executed, of 10\%.
They write in their research that it is limited to the mutator operators on expression level. 
If a mutator did not generate two or more mutants they could not detect overlapping mutants.
Their future work includes adding more mutators and widening the scope level to statements or blocks.
\newline
The research does not include efficiency.
While they show that they can cluster mutants based on overlap they do not show how efficient the mutation testing process is compared to executing a full set of mutants.
A threat to their validity, which is not addressed, is the fact that two overlapping mutants may not be challenged by the same tests and thus can result in different results.
Our research solves this problem by taking into account the location of the mutants.
Chapter \ref{ch:characteristics_location} describes what characteristics we use.

\section{Clustering by scope}
Yu et al., extended the research about overlapping mutants(See chapter \ref{ch:overlapping_mutants})\cite{Yu2019PossibilityScope}.
They extended the scope by adding more mutators.
The also extended the research to include statements and blocks.
Their results shows an increase in clustered mutants.
The research of Yu et al., suffers from the same limitations and threats  mentioned in Chapter \ref{ch:overlapping_mutants}.

\section{Clustering Hamming distance}
Ji et al., did a qualitative domain analysis on mutants\cite{Ji2009}.
As a result they identified the Hamming distance to cluster with. 
The Hamming distance is, like the Levenshtein distance, a similarity measure.
They use the k-means algorithm to cluster mutants represented by Hamming distance.
They write that the reduced test set in their experiment is still as strong as the original test set\cite{Ji2009}.
\newline
Ji et al., were successful in clustering mutants with Hamming distance and the k-means algorithm.
They do acknowledge that their research still has problems with rationally determining the domains of their clusters.
Our research does not have this problem, as the centre of the domains are decided by the characteristics of the mutants.

\section{Spectral clustering}
Wei et al., makes use of an intelligent technique, namely spectral clustering, to improve the efficacy of mutant reduction\cite{Wei2021SpectralTesting}.
They defined multiple definitions for the mutants; similarity distance, distance between the mutants and a killing matrix of the mutants.
With these definitions they reduced the mutants based on their proposed reduction method.
This method is based on spectral clustering (SCMT), the determination method of the number of clusters, spectral clustering of mutants, and selection of representative mutants.
The reduced mutants were then clustered with a classical clustering algorithm.
Their results are promising and show high cluster accuracy.
They write that there is still work left to do in optimizing the matrices and clustering algorithms.
Our goal overlaps with that of Wei, the difference is that we used a different methodology to achieve that goal.
Another difference is that our research does not require to know the result of a mutant(killed or survived).

\section{Clustering similarity}
Hussain et al., used the k-means and agglomerative clustering algorithm to cluster the mutants according to a similarity measure. 
They used the Hamming distance as similarity measure.
They calculated the distance and used this as data to feed into the clustering algorithms.
The number of clusters and the initial position of the cluster center in the k-means algorithm are difficult to determine, and the process of the agglomerative clustering algorithm makes it difficult to correct the existing cluster formation\cite{Hussain2008}.
They did take into account efficiency.
Hussain et al, had the same goals as our research. 
The difference is that our research used different and more elaborated methods to cluster the mutants.
Hussain et al., calculated the mutation score by counting one cluster as one mutant.
Our research calculated a weighted mutation score to reflect the clusters more accurately.

\section{Generalizing mutants}
Wilinski et al., tried to generalize the mutants by defining metrics.
Each metric is calculated for a specific mutator.
The three metrics are usefulness, frequency and dependency.
Combining the results of usefulness and frequency metrics, they observed that reducing the number of generated mutants gives noticeable cost reduction without a loss of the mutation score accuracy.
Wilinski et al., their research is narrowly scoped to the specific mutators they decided to do research on.
Our research does not contain this limitation.
The mutator is used as a characteristic in our research instead of limiting our research it helps define a mutant.

### 2021-07-17 chapters/7_experiment_design.tex
minor changes

\subsection{Weighted mutation score}
\label{ch:weighted_score}
Our hypothesis states that each mutants executed should represent that whole cluster.
With a mutant executed from each cluster we can calculate a mutation score.
This mutation score is a weighted mutation score.
This weighted mutation score is the product of the result of a mutant(1 for killed and 0 for survived) and the amount of mutants in the cluster it represents.
The weighted mutation score is then comparable to the score of a full set as the total number of mutants will be the same.
\newline
For example, take a full set with a score of 75/100 killed mutants.
This gives us a mutation score of 75\%. 
We then cluster the mutants in four clusters consisting of 12, 30, 38 and 20 mutants, respectively.
We randomly select four mutants of each cluster and execute them.
The mutants representing cluster one and four survive and two and three are killed.
If we calculate the weighted score we get 68/100 which is 68\%.
We can then compare this to the score of a full set because the amount of mutants executed is the same: 75/100(75\%) and 68/100(68\%).

\section{Validation}
\label{ch:exp1_validation}
The most efficient way to measure test effectiveness with mutation testing is by executing all mutants that a mutation testing tool can possibly generate.
The goal of this experiment is to reduce the amount of mutants executed while maintaining effectiveness.
To reduce the amounts executed we cluster the mutants. 
We can measure this by counting the number of clusters we generate and compare it to the number of total mutants generated by the selected tool.
\newline
To validate how effective our method of clustering is we can compare the weighted mutation score(see Chapter \ref{ch:weighted_score}) of the clustered set to the mutation score of the full set.
The closer the weighted score is to that of a full set the more effective our set of characteristics and clustering algorithm proves to be.
In other words we want achieve a mutation score that is as close as possible as to that of a full set.
We select a statistical significance level of $\leq 0.05$.
This is the conventional threshold for declaring statistical significance\cite{Kirk1996PracticalCome}.
\newline
Depending on the effectiveness of our clustering algorithm we may loose accuracy.
This can happen if a cluster contains mutants of both results. 
We can measure the accuracy inside a cluster by calculating a percentage of all mutants that have survived against the ones that have been killed in a cluster.
If the majority of the mutants in a cluster is killed then we consider that cluster to represent a killed cluster and the other way around for survived mutants.
We consider the mutants that are not in the majority of the cluster as inaccuracy.
\newline
If the weighted mutation score of our clustered set deviates more than 5\% from the score of a full set we will reject our hypothesis.

>>>>

\section{Weighted mutation score}
\label{ch:weighted_score}
Our hypothesis states that each mutant executed should represent that whole cluster.
With a mutant executed from each cluster we can calculate a mutation score.
This mutation score is a weighted mutation score.
This weighted mutation score is the product of the result of a mutant(1 for killed and 0 for survived) and the amount of mutants in the cluster it represents.
The weighted mutation score is then comparable to the score of a full set as the total number of mutants will be the same.
\newline
For example, take a full set with a score of 75/100 killed mutants.
This gives us a mutation score of 75\%. 
We then cluster the mutants in four clusters consisting of 12, 30, 38 and 20 mutants, respectively.
We randomly select four mutants of each cluster and execute them.
The mutants representing cluster one and four survive and two and three are killed.
If we calculate the weighted score we get 68/100 which is 68\%.
We can then compare this to the score of a full set because the amount of mutants executed is the same: 75/100(75\%) and 68/100(68\%).

\section{Validation}
\label{ch:exp1_validation}
The most efficient way to measure test effectiveness with mutation testing is by executing all mutants that a mutation testing tool can possibly generate.
The goal of this research is to reduce the amount of mutants executed while maintaining effectiveness.
To reduce the amounts executed we cluster the mutants. 
We can measure this by counting the number of clusters we generate and compare it to the number of total mutants generated by the selected tool.
\newline
To validate how effective our method of clustering is we can compare the weighted mutation score(see Chapter \ref{ch:weighted_score}) of the clustered set to the mutation score of the full set.
The closer the weighted score is to that of a full set the more effective our set of characteristics and clustering algorithm proves to be.
In other words we want achieve a mutation score that is as close as possible as to that of a full set.
We select a statistical significance level of $\leq 0.05$.
This is the conventional threshold for declaring statistical significance\cite{Kirk1996PracticalCome}.
\newline
Depending on the effectiveness of our clustering algorithm we may loose accuracy.
This can happen if a cluster contains mutants of both results. 
We can measure the accuracy inside a cluster by calculating a percentage of all mutants that have survived against the ones that have been killed in a cluster.
If the majority of the mutants in a cluster is killed then we consider that cluster to represent a killed cluster and the other way around for survived mutants.
We consider the mutants that are not in the majority of the cluster as inaccuracy.
\newline
If the weighted mutation score of our clustered set deviates more than 5\% from the score of a full set we will reject our hypothesis.

### 2021-07-17 chapters/rq2/1_clustering_mutants.tex
minor changes

\subsection{Self organizing map, C-means and \acrlong{fcm}}
\label{ch:topThreeModels}
The \acrfull{som}, C-means and \acrfull{fcm} models are all models that would fit our purpose. 
To choose between these models we will look at the performance of each model.
Mingoti et al., compared the performance of these three models \cite{Mingoti2006ComparingAlgorithms}.
They did a Monte Carlo simulation where the cluster sizes and amount of random numbers in the data set varied each simulation\cite{Mingoti2006ComparingAlgorithms}.
Other variables such as cluster boundaries and overlap were also controlled variables in the experiment.
They observe that the C-means and \acrlong{fcm} had good performance for non overlapping situations\cite{Mingoti2006ComparingAlgorithms}.
The best results for average recovery and internal dispersion rates were found for \acrlong{fcm} which was stable in all situations achieving recovery averages over 90\%\cite{Mingoti2006ComparingAlgorithms}
The C-means method was affected by the presence of a large amount of outliers.
They conclude that the \acrshort{som} did not perform well in many cases being affected by the amount of variables and clusters even for the non overlapping cases\cite{Mingoti2006ComparingAlgorithms}.
They also observe  that their results partially overlap with other research in the same domain.
\newline
Based the conclusions made by Mingoti et al., we can conclude that the \acrshort{fcm} model has the best performance overall.
Thus for this experiment we select the \acrshort{fcm} model.

@@

\section{Algorithm parameters}
The \acrshort{fcm} algorithm has to initialize the centroids of the clusters.
The library we selected does this based on a random number.
It also allows us to control this random number.
To make the initialization of the centroid reproducible we will use the same generated seeds as in our first experiment.
The seeds generated are included in the Github repository\cite{rbasarat-repo}.
\newline
Bezdek et al., also researched cluster validity for the \acrshort{fcm} model\cite{Bezdek1995OnModel}.
They researched what effect which parameters could have on the validity of the clusters.
They specifically analyzed the role of weighting exponent \textit{m}(fuzziness parameter).
They concluded that the best choice for \textit{m} is in the interval [1.5, 2.5], whose mean and midpoint is \textit{m}=2.
Wu proposed a new guideline for selecting parameter \textit{m}\cite{Wu2012}.
His point of view was that a large \textit{m} value will make the \acrlong{fcm} more robust to noise and outliers.
He suggests implementing \acrlong{fcm} with \textit{m}=[1.5, 4].
When the data set contains noise and outliers, the fuzzifier \textit{m}=4 is recommended in a theoretical upper bound case.
Since our data set does not contain noise we choose to select the midpoint concluded in the research of Bezdek et al.\cite{Bezdek1995OnModel}.
The value of \textit{m} in this experiment is 2.
\newline
Finding the correct amount of clusters has been an ongoing problem for clustering algorithms\cite{Du2010Clustering:Approach}.
Fortunately there are techniques available to estimate the number of clusters.
During model selection we discussed the mountain and subtractive models. 
These models are designed to estimate the number of clusters in a data set.
The subtractive clustering model is specifically designed to approximate the number of clusters for fuzzy system models\cite{Chiu1994FuzzyEstimation}.
It approximates the centroids and amount of the clusters based on the data points in the data set\cite{Chiu1994FuzzyEstimation}.
We will select and implement the subtractive clustering model to estimate the number of clusters.
We will use this number as the value for the number of clusters parameter in the \acrshort{fcm} algorithm.

>>>>

\subsection{Self organizing map, C-means and fuzzy c-means}
\label{ch:topThreeModels}
The \acrfull{som}, C-means and \acrfull{fcm} models are all models that would fit our purpose. 
To choose between these models we will look at the performance of each model.
Mingoti et al., compared the performance of these three models \cite{Mingoti2006ComparingAlgorithms}.
They did a Monte Carlo simulation where the cluster sizes and amount of random numbers in the data set varied each simulation\cite{Mingoti2006ComparingAlgorithms}.
Other variables such as cluster boundaries and overlap were also controlled variables in the experiment.
They observe that the C-means and \acrlong{fcm} had good performance for non overlapping situations\cite{Mingoti2006ComparingAlgorithms}.
The best results for average recovery and internal dispersion rates were found for \acrlong{fcm} which was stable in all situations achieving recovery averages over 90\%\cite{Mingoti2006ComparingAlgorithms}
The C-means method was affected by the presence of a large amount of outliers.
They conclude that the \acrshort{som} did not perform well in many cases being affected by the amount of variables and clusters even for the non overlapping cases\cite{Mingoti2006ComparingAlgorithms}.
They also observe  that their results partially overlap with other research in the same domain.
\newline
Based the conclusions made by Mingoti et al., we can conclude that the \acrshort{fcm} model has the best performance overall.
Thus for this experiment we select the \acrshort{fcm} model.

@@

\section{Algorithm parameters}
The \acrshort{fcm} algorithm has to initialize the centroids of the clusters.
The library we selected does this based on a random number.
It also allows us to control this random number.
To make the initialization of the centroid reproducible we will use the same generated seeds as in our first experiment.
The seeds generated are included in the Github repository\cite{rbasarat-repo}.
\newline
Bezdek et al., also researched cluster validity for the \acrshort{fcm} model\cite{Bezdek1995OnModel}.
They researched what effect which parameters could have on the validity of the clusters.
They specifically analyzed the role of weighting exponent \textit{m}(fuzziness parameter).
They concluded that the best choice for \textit{m} is in the interval [1.5, 2.5], whose mean and midpoint is \textit{m}=2.
Wu proposed a new guideline for selecting parameter \textit{m}\cite{Wu2012}.
His point of view was that a large \textit{m} value will make the \acrlong{fcm} more robust to noise and outliers.
He suggests implementing \acrlong{fcm} with \textit{m}=[1.5, 4].
When the data set contains noise and outliers, the fuzzifier \textit{m}=4 is recommended in a theoretical upper bound case.
Since our data set does not contain noise(all mutants consists of every characteristic) we choose to select the midpoint concluded in the research of Bezdek et al.\cite{Bezdek1995OnModel}.
The value of \textit{m} in this experiment is 2.
\newline
Finding the correct amount of clusters has been an ongoing problem for clustering algorithms\cite{Du2010Clustering:Approach}.
Fortunately there are techniques available to estimate the number of clusters.
During model selection we discussed the mountain and subtractive models. 
These models are designed to estimate the number of clusters in a data set.
The subtractive clustering model is specifically designed to approximate the number of clusters for fuzzy system models\cite{Chiu1994FuzzyEstimation}.
It approximates the centroids and amount of the clusters based on the data points in the data set\cite{Chiu1994FuzzyEstimation}.
We will select and implement the subtractive clustering model to estimate the number of clusters.
We will use this number as the value for the number of clusters parameter in the \acrshort{fcm} algorithm.
